---
title: "Manhattan Real Estate Condominium Sales Price Analysis"
author: "Jiaoyan Zhang"
date: "March 24, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R 
## Correlations
Correlation between Dependent Variable Price and Independent variables Bath,Bed,Tax/Mo,CC/Mo and Int#SF
```{r, echo=FALSE,na.rm=TRUE}
df <- read.csv("Manhattan Wide_Unit Level.csv", header = TRUE)
#save(df, file = "df1.RData")
#load(file="df1.RData")

#exclude RM and AS units
df <- subset(df, Unit.Type!="as" & Unit.Type!="rm")
df <- subset(df, Sales.Start.Year>2011)
str(df)
```

```{r, echo=FALSE,na.rm=TRUE}
res <- cor(df[,c(1,7,11,12,13,14,16,24,27,28,29,30,31)],use="na.or.complete",method="pearson")
round(res, 2)

#cor(df$Price,df$Bath,use="na.or.complete",method="pearson")
#cor(df$Price,df$Bed,use="na.or.complete",method="pearson")
#cor(df$Price,df$`Tax/Mo#`,use="na.or.complete",method="pearson")
#cor(df$Price,df$`CC/Mo`,use="na.or.complete",method="pearson")
#cor(df$Price,df$`Int# SF`,use="complete.obs",method="pearson")
```

```{r}

mean(df$Price,na.rm=TRUE)
min(df$Price,na.rm=TRUE)
max(df$Price,na.rm=TRUE)
mean(df$Bed,na.rm=TRUE)
mean(df$Bath,na.rm=TRUE)
mean(df$`Int..SF`,na.rm=TRUE)
mean(df$`Tax.Mo.`,na.rm=TRUE)
sd(df$Bed,na.rm=TRUE)
sd(df$Bath,na.rm=TRUE)
sd(df$`Int..SF`,na.rm=TRUE)
sd(df$`Tax.Mo.`,na.rm=TRUE)

str(df$Submarket)
```

## Multiple Linear Regression Model 
We have chosen Multiple Linear regression Model to analyze the hypothesis we made for the condominium sales price. The variables we are using to build the model are: Maintenance fee X1(cc/mo);number of bedrooms X2(Bed); number of bathrooms X3(Bath); Interior square feet X4(Int# SF); Tax per month X5(Tax/Mo)  
Price=C0 + C1*X1 + C2*X2 + C3*X3 + C4*X4 + C5*X5 

```{r}
fit1 <- lm(Price ~ Submarket+Floors+Bed+Bath +`Int..SF`+`Ext..SF`+Tax.Mo.+`Unit.Type`+POOL+SPA+GARAGE+FITNESS.CENTER+DOORMAN, data=df)
summary(fit1)
summary.aov(fit1)
```

```{r}
fit2 <- lm(Price ~ Submarket+Floors+Bath +`Int..SF`+`Ext..SF`+Tax.Mo.+`Unit.Type`+POOL+FITNESS.CENTER, data=df)
summary(fit2)
summary.aov(fit2)
```

```{r}
fit3 <- lm(Price ~ Submarket+Floors+Bath +`Int..SF`+`Ext..SF`+Tax.Mo.+`Unit.Type` + Sold.Year+POOL+FITNESS.CENTER, data=df)
summary(fit3)
summary.aov(fit3)
```